Supplemental Information

### 2015-01-29 image_analysis_paper_development2/SI_text.tex
updated code and paper

>>>>

The original image resolution is $512 \times 512$ for the live {\em Drosophila} images, $320 \times 288$ for the zebrafish images, $1024 \times 1024$ for the fixed {\em Drosophila} images, and $1024 \times 1024$ for each of the images in the wing disc z-stacks. 
%
Each of the original wing disc z-stacks contains 30--40 images.

All images were subsampled to $100 \times 100$ pixels for analysis, as this was found to be a sufficient resolution to retain all of the major developmental features within the data set. 
%
Each wing disc z-stack was reduced to a 21-image stack, consisting of the brightest image and the 10 images above and below.

The relevant image operations are 
\begin{enumerate}
\item {\bf Intensity normalization:} Contrast-limited adaptive histogram equalization (using the \texttt{adapthisteq} function with an $8 \times 8$ tile grid, and a uniform distribution for the intensities with a clip limit of 0.01) is used to normalize the intensities of the nuclear signal.
\item {\bf Blur} Using the \texttt{imfilter} function. 
\item {\bf Intensity scaling} 
\item {\bf Mean-centering} 
\item {\bf Size scaling}
\item {\bf Removing corners}
\end{enumerate}
